### 2021-06-03 code/manuscript.Rmd
add new plot, sourceloc

```{r setup, include=FALSE}
# Load packages
library(MASS)
library(lme4)
library(buildmer)
library(emmeans)
library(brms)
library(parallel)
library(reticulate)
library(papaja)
library(cowplot)
library(scales)
library(tidyverse)
library(magrittr)

@@

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- FALSE
rerun_model_fitting <- TRUE

@@

# File names for easier I/O
fnames <- list(
  montage = "data/processed/montage.csv",
  objects_per_condition = "data/processed/obj-per-cond.csv",
  evo_gavg = "data/processed/evo_gavg.csv",
  evo_tfr_flat = "data/processed/evo-tfr_flat.csv",
  evo_tfr_diff = "data/processed/evo-tfr_diff.csv",
  evo_tfr_flat_nochans = "data/processed/evo-tfr_flat-nochans.csv",
  evo_tfr_diff_nochans = "data/processed/evo-tfr_diff-nochans.csv",
  models_freq = "data/processed/models_freq.RDS"
)
```

@@

  # Get standard EasyCap electrode positions and project them into 2D space
  dir.create("data/processed")
  read_csv("data/preprocessed/sub-01_tfr-evo.csv", col_types = cols()) %>%
    select(-c(part, condition, subject_id, time, freq)) %>%
    colnames() -> ch_names
  import("mne.channels._standard_montage_utils")$MONTAGE_PATH %>%
    paste0("/easycap-M1.txt") %>%
    read_tsv(col_types = cols()) %>%
    rename(electrode = Site) %>%
    inner_join(tibble(electrode = ch_names), ., by = "electrode") %>%
    mutate(
      x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
      y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
    ) %>%
    mutate(across(c(x, y), round, 3)) %>%
    write_csv(fnames$montage)

@@

# Read evoked *potentials* for all subjects
fname_evo_tfr = ["data/preprocessed/" + sub + "_evo.csv" for sub in r.subject_id]
evo = [pd.read_csv(fname) for fname in fname_evo_tfr]
evo = pd.concat(evo)

@@

# Read evoked *power* for all subjects
fname_evo_tfr = ["data/preprocessed/" + sub + "_tfr-evo.csv" for sub in r.subject_id]
evo_tfr = [pd.read_csv(fname) for fname in fname_evo_tfr]
evo_tfr = pd.concat(evo_tfr)

@@

```{r, models_freq}
# Read single trial data for all subjects
paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
  map(read_csv, col_types = cols()) %>%
  bind_rows() %>%
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c("Informed", "Naive")),
    subject_id = factor(subject_id),
    item_id = factor(item_id),
    RT = ifelse(RT < 200, NA, RT),
    logRT = log(RT)
  ) -> trials

@@

  # Load models
  models_freq <- readRDS(fnames$models_freq)
} else {

@@

    # Save
    set_names(dvs) %T>%
    saveRDS(fnames$models_freq) -> models_freq
}

please_stop_here()
```

```{r models_bayes, eval=FALSE}
# Define model formula
form <- P1 ~ part * condition +
  (part * condition | subject_id) +
  (part * condition | item_id)

@@

# Fit Bayesian mixed model
mod_brm <- brm(
  formula = form,
  data = trials,
  family = gaussian(),
  prior = prior,
  sample_prior = "yes",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  # iter = 20000,
  # warmup = 2000,
  # cores = 4,
  backend = "cmdstanr"
)

@@

```{r fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
# Load montage and data
montage <- read_csv(fnames$montage, col_types = cols())
evokeds <- read_csv(fnames$evo_gavg, col_types = cols())
models_freq <- readRDS(fnames$models_freq)

# Create plot for Experiment 1
plot_grid(
  plot_trials(),
  plot_erps(erp_components, evokeds, models_freq, montage),
  nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
) + # Add some lines (to separate the parts) and the legend
  annotate_line(x = 0.328, xend = 0.328, y = -Inf, yend = 0.53) +
  annotate_line(x = 0.672, xend = 0.672, y = -Inf, yend = 0.53) +
  annotate_line(x = 0.328, xend = 0.28, y = 0.53, yend = 0.58) +
  annotate_line(x = 0.672, xend = 0.72, y = 0.53, yend = 0.58) +
  annotate_line(x = 0.28, xend = 0.28, y = 0.58, yend = Inf) +
  annotate_line(x = 0.72, xend = 0.72, y = 0.58, yend = Inf) +
  draw_plot(
    plot_legends_erps(direction = "vertical"),
    x = 0.405, y = 0.422, width = 1, height = 1
  )
```

>>>>

```{r setup, include=FALSE}
# Load packages
library(MASS)
library(lme4)
library(buildmer)
library(emmeans)
library(brms)
library(parallel)
library(reticulate)
library(magick)
library(papaja)
library(cowplot)
library(scales)
library(tidyverse)
library(magrittr)

@@

# Re-run preprocessing and/or model fitting?
rerun_preprocessing <- TRUE
rerun_model_fitting <- FALSE

@@

# File names for easier I/O
fnames <- list(
  montage = "results/montage.csv",
  objects_per_condition = "results/obj-per-cond.csv",
  evo_gavg = "results/evo_gavg.csv",
  evo_tfr_flat = "results/evo-tfr_flat.csv",
  evo_tfr_diff = "results/evo-tfr_diff.csv",
  models_lme = "results/models_lme.RDS"
)
```

@@

  # Get standard EasyCap electrode positions and project them into 2D space
  dir.create("data/processed")
  read_csv("data/preprocessed/sub-01_tfr-ave.csv", col_types = cols()) %>%
    select(-c(part, condition, subject_id, time, freq)) %>%
    colnames() -> ch_names
  import("mne.channels._standard_montage_utils")$MONTAGE_PATH %>%
    paste0("/easycap-M1.txt") %>%
    read_tsv(col_types = cols()) %>%
    rename(electrode = Site) %>%
    inner_join(tibble(electrode = ch_names), ., by = "electrode") %>%
    mutate(
      x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
      y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
    ) %>%
    mutate(across(c(x, y), round, 3)) %>%
    write_csv(fnames$montage)

@@

# Read evoked *potentials* for all subjects
fname_evo_tfr = ["data/preprocessed/" + sub + "_ave.csv" for sub in r.subject_id]
evo = [pd.read_csv(fname) for fname in fname_evo_tfr]
evo = pd.concat(evo)

@@

# Read evoked *power* for all subjects
fname_evo_tfr = ["data/preprocessed/" + sub + "_tfr-ave.csv" for sub in r.subject_id]
evo_tfr = [pd.read_csv(fname) for fname in fname_evo_tfr]
evo_tfr = pd.concat(evo_tfr)

# Subject 18 is weird!
evo_tfr = evo_tfr[evo_tfr["subject_id"] != "sub-18"]

@@

```{r, models_lme}
# Read single trial data for all subjects
paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
  map(read_csv, col_types = cols()) %>%
  bind_rows() %>%
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c("Informed", "Naive")),
    subject_id = factor(subject_id),
    item_id = factor(item_id),
    RT = ifelse(RT < 200, NA, RT),
    logRT = log(RT)
  ) -> trials

@@

  # Load models
  models_lme <- readRDS(fnames$models_lme)
} else {

@@

    # Save
    set_names(dvs) %T>%
    saveRDS(fnames$models_lme) -> models_lme
}
```

```{r models_brm, eval=FALSE}
# Color scheme for plots
bayesplot::color_scheme_set("purple")

# Define model formula
formula_brm <- P1 ~ part * condition +
  (part * condition | subject_id) +
  (part * condition | item_id)

@@

# Fit Bayesian mixed model using prior information only
mod_brm_prior <- brm(
  formula = formula_brm,
  data = trials,
  family = gaussian(),
  prior = prior,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = 20000,
  warmup = 2000,
  backend = "cmdstanr"
)

# Prior predictive checks for population-level parameters
prior_summary(mod_brm_prior)
summary(mod_brm_prior)
mcmc_plot(mod_brm_prior, "areas", pars = "^b_", prob_outer = 0.95) +
  theme(text = element_text(family = "Helvetica", size = 10))

# Refit using the actual data
mod_brm_posterior <- update(mod_brm_prior, sample_prior = "yes")

# Posterior predictive checks for population-level parameters
summary(mod_brm_posterior)
mcmc_plot(mod_brm_posterior, "areas", pars = "^b_", prob_outer = 0.95) +
  theme(text = element_text(family = "Helvetica", size = 10))

# Posterior predictive checks subject by subject
pp_check(
  mod_brm_posterior,
  type = "dens_overlay_grouped",
  nsamples = 50,
  group = "subject_id"
)
pp_check(
  mod_brm_posterior,
  type = "stat_grouped",
  nsamples = 1000,
  group = "subject_id",
  stat = "sd"
)

# Post-hoc comparisons for informed vs. naive within each part
hyps <- c(
  "posthoc_1" = "condition1 - 2/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
  "posthoc_2" = "condition1 + 1/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
  "posthoc_3" = "condition1 + 1/3 * part1:condition1 + 2/3 * part2:condition1 = 0"
)
hypothesis(mod_brm_posterior, hyps) %>%
  mutate(.$hypothesis, bf01 = Evid.Ratio, bf10 = 1 / Evid.Ratio, .keep = "unused")

# Alternative with emmeans
specs <- pairwise ~ condition | part
emmeans(mod_brm_posterior, specs = specs)

@@

```{r fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
# Load montage and evoked data
montage <- read_csv(fnames$montage, col_types = cols())
evokeds <- read_csv(fnames$evo_gavg, col_types = cols())

# Create plot for Experiment 1
plot_fig1(erp_components, evokeds, trials, models_lme)
```
